### 2014-01-23 Studies/Chicago_2012/Report/Chicago_Fire.tex
Update to Chicago writeup

\chapter{Introduction}

@@

On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a death of a fire captain and injury to a fire fighter.  At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''.   Within a minute of dispatch, a Battalion Chief (BC) arrived and sized up the structure fire from the exterior and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.  After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.  Engine 123 arrived on scene at approximately 5:19. The victims were part of the Engine 123 crew.  The BC met the Captain and the Fire Fighter (victims) at the front door to the structure.  Then the Captain and Fire Fighter took their hose line to the second floor of the structure.  At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.   Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL 39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.   The fire fighter from TL 39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.   Both doors remain open and the fire fighter from TL 39 exits the structure.  Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the Engine 123 Captain at 5:23, to alert him to the fire conditions and to advise him that Engine 49 would be applying water to the fire on the rear of the structure from the exterior.  No response was made by the Engine 123 Captain.  It is believed that the door between the rear porch and the second floor hallway, where the Engine 123 Captain and Fire Fighter were located may have failed by this time.  Approximately a minute later Engine 49 applied water to the fire in the attic.

>>>>

\chapter{Introduction}
Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements and standards, improve the understanding of the behavior, prevention and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response. NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other fatality fires \cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}. The overriding objective of all of these studies is to improve the safety of fire fighters.

On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure claimed the life of a Chicago firefighter.  Changes in the ventilation flow path cause a rapid change in the fire dynamics resulting in fire and smoke penetration to an interior second floor hallway. NIST assisted with examining the fire dynamics of this incident. NIST performed computer simulations of the fire using the FDS and Smokeview, a visualization tool, to provide insight on the fire development and thermal conditions that may have existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine with physics-based calculations the effect of flow path on the thermal and fire conditions in this multi-story residential structure.
\item To provide visualization of fire behavior representative of what Chicago Fire Department members experienced during the course of their interior operations.
\end{enumerate}
This document describes the input and the results of the FDS (version 6.0.0) simulations.

@@

On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a fire captain and injury to a fire fighter.  At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''.   Within a minute of dispatch, a Battalion Chief (BC) arrived and sized up the structure fire from the exterior and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.  After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.  Engine 123 arrived on scene at approximately 5:19. The victims were part of the Engine 123 crew.  The BC met the Captain and the Fire Fighter (victims) at the front door to the structure.  Then the Captain and Fire Fighter took their hose line to the second floor of the structure.  At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.   Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL 39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.   The fire fighter from TL 39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.   Both doors remain open and the fire fighter from TL 39 exits the structure.  Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the Engine 123 Captain at 5:23, to alert him to the fire conditions and to advise him that Engine 49 would be applying water to the fire on the rear of the structure from the exterior.  No response was made by the Engine 123 Captain.  It is believed that the door between the rear porch and the second floor hallway, where the Engine 123 Captain and Fire Fighter were located may have failed by this time.  Approximately a minute later Engine 49 applied water to the fire in the attic.
